### 2021-03-25 newvariant.tex
more tweaks

The integral of the kernel $\RR_x(t) = \int K_x(t, \tau) \dtau$---referred to as the instantaneous reproduction number---describes the average infectiousness of previously infected individuals at time $t$ \citep{fraser2007estimating}.
\jd{This is a particular kind of weighted average – in particular, it's not weighted by the actual number of infected individuals present. I kind of want to say GI-weighted average, but then we would have to introduce GI as an abbrv.}
The normalized kernel $g_x(t, \tau) = K_x(t, \tau)/\RR_x(t)$---which we refer to as the instantaneous generation-interval distribution---describes their relative contribution to current incidence $i_x(t)$ and provides information about the time scale of disease transmission.
Both the reproduction number and the generation-interval distribution can depend on several factors, including intrinsic infectiousness of an infected individual, non-pharmaceutical interventions, awareness-driven behavior, and population-level susceptibility \citep{fraser2007estimating}.

>>>>

The integral of the kernel $\RR_x(t) = \int K_x(t, \tau) \dtau$ is referred to as the instantaneous reproduction number \citep{fraser2007estimating}.
This is a particular kind of weighted average which describes the average infectiousness of previously infected individuals at time $t$---in particular, it is not weighted by the actual number of infected individuals present, but rather by their relative infectiousness at time $t$.
The normalized kernel $g_x(t, \tau) = K_x(t, \tau)/\RR_x(t)$---which we refer to as the instantaneous generation-interval distribution---describes their relative contribution to current incidence $i_x(t)$ and provides information about the time scale of disease transmission.
Both the reproduction number and the generation-interval distribution can depend on several factors, including intrinsic infectiousness of an infected individual, non-pharmaceutical interventions, awareness-driven behavior, and population-level susceptibility \citep{fraser2007estimating}.
